---
title: "Arendsee Experiment"
author: "Harm van Kuppevelt"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE)
```


# import and libraries
```{r packages, include=FALSE}
library(readxl)
library(tidyverse)
library(ggplot2)

```

First import all raw data. The concentrations of P, Fe and Mn in the extraction solutions, and the Dryweight data.
```{r import}
conc_2month_raw <- read_xlsx("20220800SequentalExtractions.xlsx")

conc_10month_raw <- read_xlsx("20230321_seqentialExtractions.xlsx")
conc_10month_raw <- pivot_longer(conc_10month_raw,5:11, names_to = "Fraction", values_to = "Conc")

conc_before_raw <- read_xlsx("BeforeSequentialExtractions.xlsx")


wt_2month_raw <- read_xlsx("20220816_AR_Dryweight.xlsx")
wt_10month_raw <- read_xlsx("20230321_AR_Dryweight.xlsx")

xrd_raw <- read_xlsx("20221018_AR_XRD.xlsx")


kwa_raw <- read_xlsx("KWA.xlsx")
kwa_raw[str_detect(kwa_raw, "<")] <- 0

```

# Total elements

```{r}
FeP <- function(Fe,P){
  FeP <- (Fe/55.845)/(P/30.97)
return(FeP)
}
FeS <- function(Fe,S){
  FeS <- (Fe/55.845)/(S/32.06)
return(FeS)
}

kwa <- kwa_raw %>% 
  filter(!is.na(depth)) %>% 
  mutate_at(5:21, ~ (.*0.05)/weight) %>% 
  group_by(time,ID) %>% 
  summarise_all(mean, keep = T) %>%  mutate(FeP = FeP(Fe,P),
         FeS = FeS(Fe,S)
         ) 

kwabefore <- kwa_2month_raw %>% 
  filter(ID == "before") %>% 
  mutate_at(5:21, ~ (.*0.05)/weight) %>% 
  select( c(ID, depth, Al, Ca, Fe, K, Mg, Mn, Na, P, Pb, S, Ti)) %>%  mutate(FeP = FeP(Fe,P), FeS = FeS(Fe,S)) 
kwabefore$depth <- 30
  
  Scalc <- kwa %>% mutate(Smol = S/mmS,
                          Femol = Fe/mmFe,
                          ratepyr = ((Smol/2))/Femol )

```


```{r}


kwalong <- select(kwa, c(time, ID, depth,FeP,FeS, Ca, Fe, P, S)) %>% 
  pivot_longer(cols = FeP:last_col(), names_to = "Parameter", values_to = "Value") %>% 
  transform(Parameter =  factor(Parameter, levels = (c("FeP","FeS", "Ca", "Fe", "P", "S")))) %>% 
  filter(time == "t2")

kwaplots <- ggplot(  kwalong, 
         mapping = aes(
           y = Value,
           x = depth,
          color = Parameter)
) +
   
  geom_line()  +
  geom_point(size = 2) +
  facet_grid(cols = vars(Parameter),rows = vars(time), scales = "free") +
  geom_point( 
    data = transform(pivot_longer(kwabefore, cols = c(FeP,FeS, Ca, Fe, P, S), names_to = "Parameter", values_to = "Value"), Parameter = factor(Parameter, levels = c("FeP","FeS", "Ca", "Fe", "P", "S"))) , 
    aes( y = Value, x = 30),
    color="black")+

  xlab("Depth (cm)") +
  scale_x_reverse() +
  coord_flip() +
  labs(  y = expression(paste("concentration mg/g")), 
         x = "Depth in cm",
         title = "element profiles" ) +
  theme_bw() +
  theme(      aspect.ratio = 2,
                  axis.title=element_text(size=8),
                  plot.title = element_text(size=20, face="bold", hjust = 0.5) ,
                  axis.text=element_text(size=8,angle = 0, hjust = 0.5),
                  legend.title = element_text(size = 8),
                  legend.text = element_text(size = 8),
                  legend.key.size = unit(1.5, "cm"))

show(kwaplots)

ggsave( "kwaplot.png", plot = kwaplots, width = 20, height = 5)

```

# Sequential Extractions




##  Data Corrections 

 Filter the values of the blanks from the concentration data, and take the mean value for each measurement series.
```{r }


blanks_2month <- filter(conc_2month_raw, is.na(Depth)) %>% 
  group_by(Fraction, Parameter, Measurement) %>%
  summarise(blank = mean(Conc), .groups = "drop") 

blanks_10month <- filter(conc_10month_raw, is.na(Depth)) %>% 
  group_by(Fraction, Measurement) %>%
  summarise(blank = mean(Conc), .groups = "drop") 

blanks_before <- filter(conc_before_raw, Nr == "blank") %>% 
  group_by(Sample,Fraction, Parameter) %>%
  summarise(blank = mean(Conc), .groups = "drop") 
```


Define porosity values for all measurements
```{r }
porosity_2month <- 
    wt_2month_raw %>% group_by(Depth) %>% summarise(porosity = mean(Porosity))
porosity_10month <- 
    wt_10month_raw %>% group_by(Depth) %>% summarise(porosity = mean(Porosity))

porosity_before <-  
    conc_before_raw %>% filter(Parameter == "porosity") %>% group_by(Sample) %>% 
      summarise(porosity = mean(Conc))
  
```

Compute percentage dryweight from volume of solution and porosity
```{r }

conc_2month <- conc_2month_raw %>% 
  left_join(porosity_2month) %>% 
  left_join(blanks_2month, by = c("Fraction","Parameter","Measurement")) %>%  
  mutate(volume = case_when(
    Fraction == "H2O" ~ 0.05,
    Fraction == "Bipy" | Fraction == "BD" ~ 0.1,
    Fraction == "NaOH" ~ 0.075,
    T ~ 0 )) %>%  
  add_column(time = "2month")

conc_10month <- conc_10month_raw %>% 
  left_join(porosity_10month) %>% 
  left_join(blanks_10month, by = c("Fraction","Measurement")) %>% 
  separate(Fraction, c("Fraction", "Parameter")) %>% 
   mutate(volume = case_when(
    Fraction == "H2O" ~ 0.02,
    Fraction == "Bipy" | Fraction == "BD" ~ 0.04,
    Fraction == "NaOH" ~ 0.03,
    T ~ 0 )) %>%  
  add_column(time = "10month")

conc <- 
  full_join(conc_10month,conc_2month) %>% 
 mutate(cont = ((Conc-blank)*volume)/(Weight*(1-porosity)),
        Depth = Depth +3)

before <- conc_before_raw %>% 
  filter ( !is.na((Weight))) %>%  
  left_join(blanks_before, by = c("Sample","Fraction","Parameter")) %>% 
  left_join(porosity_before, by = "Sample") %>%
  mutate(volume = case_when(
    Nr == "5"~ 0.150,
    Sample == "30-35" &  Fraction == "H2O" ~ 0.05,
    Sample == "30-35" &  (Fraction == "Bipy" | Fraction == "BD") ~ 0.1,
    Sample == "30-35" &  Fraction == "NaOH" ~ 0.075,
    Sample == "Before" &  Fraction == "H2O" ~ 0.02,
    Sample == "Before" &  (Fraction == "Bipy" | Fraction == "BD") ~ 0.04,
    Sample == "Before" &  Fraction == "NaOH" ~ 0.03,
    T ~ 0 ))%>%  
  mutate(cont = (((Conc)-blank)*volume)/(Weight*(1-porosity)),
         species = paste(Fraction, Parameter),
         time = "before")
  

beforevalues <- before %>%   
  filter( Parameter == "TP" | Parameter == "SRP" ) %>% 
  mutate( Fraction = paste(Fraction, Parameter)  ) %>% 
  group_by(time, Sample, Fraction) %>% 
  summarise( stdev = sd(cont), cont = mean(cont) )


  add_row(Fraction = "Total", stdev = 0, cont = pull(  
  summarise_all(group_by(kwabefore, ID), mean), "P"))

before_plot <- ggplot(filter(before, Parameter == "TP" | Parameter == "SRP"), aes(x=species, y = cont, fill=Sample)) +
  geom_boxplot(position=position_dodge(1))
show(before_plot)

```

## P data analysis
Just P
```{r}

Pdata <- filter(remove_missing(conc), (Parameter == "TP" | Parameter == "SRP") & Fraction != "BD")

Pdata$Fraction <- factor(Pdata$Fraction)
summary(lm( cont ~ Weight, data = Pdata[Pdata$Fraction == "Bipy",] ))


weighplots <- ggplot( filter(remove_missing(conc) #, (Parameter == "TP" | Parameter == "SRP") ), 
               ),
         mapping = aes(
           y = cont,
           x = Weight,
           color = Fraction)
) +
geom_point(size = 2) +
  geom_smooth(method='lm') +
   facet_grid(rows = vars(Parameter), scales = "free") +
  labs(  y = expression(paste("conc(mg/gdw)")), 
         x = "subsample weight",
         title = "analysis " )
show(weighplots)

ggsave( "weighplot.png", plot = weighplots, width = 10, height = 20)


```

##   Analyze Bipy measurements

Filter and group bipy data by measurement type (acidified or not, TP or SRP) and avarage for each depth.
```{r }
bipy <- filter(conc, Fraction == "Bipy" ) %>%  
  filter( Parameter == "TP" | Parameter == "SRP" ) %>% 
  remove_missing() %>% 
  mutate(Parameter = case_when(
    time == "10month" ~ "TP 10month",
    Parameter == "TP" & Measurement <= 4 ~ "TPnoacid",
    Parameter == "TP" & Measurement >= 9 ~ "TP block",
    Parameter == "TP" & Measurement > 4 & Measurement < 9 ~ "TPacidified",
    T ~ "SRP"
    )) %>% 
  group_by(Parameter,  Depth) %>% 
  summarise(stdev = sd(cont), cont = mean(cont) ) 

bipytot <- filter(conc, Fraction == "Bipy" ) %>%  
  filter( (Parameter == "TP" & Measurement >4 )| Parameter == "SRP" ) %>% 
  remove_missing() %>% 
  group_by( Depth) %>% 
  summarise(stdev = sd(cont), cont = mean(cont) ) 

beforebipy <- filter(before, Fraction == "Bipy") %>%  
  filter( Parameter == "TP" | Parameter == "SRP" ) %>% 
  group_by(Sample, species) %>% 
  summarise( stdev = sd(cont), cont = mean(cont) ) 
```

Plot of the bipy profiles, by measurement type.
```{r }
ggplot( bipy, 
         mapping = aes(
           y = cont,
           color = Parameter,
           x = Depth )
) +
   
  geom_line( aes(
           y = cont,
           x = Depth ,
           shape = factor(Parameter)))  +
geom_point(size = 2) +
  #geom_errorbar(aes(ymin=cont-stdev, 
  #                  ymax=cont+stdev,
   #                 color = Parameter,), width=.2,
   #             position=position_dodge(0.05))+
  geom_point( data = beforebipy, aes( y = cont, x = 0,color = Sample) ) +
  xlab("Depth (cm)") +
  scale_x_reverse() +
  coord_flip() +
  labs(  y = expression(paste("concentration (mg/g dw)")), 
         x = "Depth in cm",
         title = "Bipy profiles" ) +
  theme_bw() +
  theme(axis.title=element_text(size=20),
                   plot.title = element_text(size=20, face="bold", hjust = 0.5) ,
                   axis.text=element_text(size=14,angle = 0, hjust = 0.5),
                   legend.title = element_text(size = 16),
                   legend.text = element_text(size = 13),
                   legend.key.size = unit(1.8, "cm"))
```
```{r }
ggplot( bipytot, 
         mapping = aes(
           y = cont,
           x = Depth )
) +
   
  geom_line()  +
geom_point(size = 2) +
  geom_errorbar(aes(ymin=cont-stdev, 
                    ymax=cont+stdev,
                    color = "St Dev",), width=.2,
                position=position_dodge(0.05))+
  geom_point( data = beforebipy, aes( y = cont, x = 0),color="black")+
  xlab("Depth (cm)") +
  scale_x_reverse() +
  coord_flip() +
  labs(  y = expression(paste("concentration (mg/g dw)")), 
         x = "Depth in cm",
         title = "Bipy profiles" ) +
  theme_bw() +
  theme(axis.title=element_text(size=20),
                   plot.title = element_text(size=20, face="bold", hjust = 0.5) ,
                   axis.text=element_text(size=14,angle = 0, hjust = 0.5),
                   legend.title = element_text(size = 16),
                   legend.text = element_text(size = 13),
                   legend.key.size = unit(1.8, "cm"))
```
##  Plot of the P sequentiallly extracted.

Define the P fractions: Select only the P measurements without blanks. For Bipy only the acidified measurements were taken.
```{r }
Pkwa <- select(kwa, depth, P) %>% 
  mutate(Fraction = "Total", stdev = 0) %>% 
  rename(Depth = depth, cont = P)

allfrac <- conc %>% select(!Nr) %>% filter(Parameter == "TP" | Parameter == "SRP") %>% 
  mutate(species = case_when(
    time == "2month" & Fraction == "Bipy" & Parameter == "TP" & Measurement >= 5 ~ NA_character_,
    Fraction == "Bipy" ~ "Bipy TP",
    T ~ paste(Fraction, Parameter)
                              )) %>%  
  remove_missing() %>% 
  full_join(mutate(filter(select(before, !Nr), (Parameter == "TP" | Parameter == "SRP"), Sample == "Before" ), Depth = 30)) %>% 
  group_by(species,  Depth, time) %>% 
  summarise(stdev = sd(cont), cont = mean(cont) ) %>% ungroup()
  
  
  bind_rows(Pkwa) 


```
```{r }
groupfrac <- allfrac %>% 
  group_by(time, species, depthgroup = cut(Depth,4)) %>% 
  summarise(stdev = sd(cont), cont = mean(cont) ) %>% filter(species != "Bipy SRP" & species != "H2O SRP" & species != "NaOH SRP") %>%  ungroup()

levels(groupfrac$depthgroup) <- c("-4-9 cm","10-22 cm", "23-35 cm", ">35 cm" )

time.labs <- c("initial sediment","2 months", "9 months")
names(time.labs) <- c("before","2month", "10month")
fraction.labs <- c("H2O","Bipy","BD","NaOH")
names(fraction.labs) <- c("H2O TP","Bipy TP","BD TP","NaOH TP")

seqextrgroup  <- 
  
  ggplot( transform( groupfrac, 
                   species = factor(species, 
                                       levels = c("H2O TP","Bipy TP","BD TP","NaOH TP")
                                       ),
                   time = factor(time, levels = (c("before","2month", "10month"))),
                   depthgroup = factor(depthgroup, levels = c(  ">35 cm","23-35 cm","10-22 cm","-4-9 cm" ))),  
                  
       aes( 
           x = depthgroup,
           y = cont,
           fill = species),
       scale_x_discrete(position = 'top' 
                        )) +
  geom_bar(
    #mapping = aes( y = cont, fill = species ),
    stat = "identity",
    position = position_dodge())+
   geom_errorbar(aes(ymin=cont-stdev, 
                   ymax=cont+stdev), width=.2,
               position=position_dodge(0.05)) +
   scale_fill_discrete(  labels = fraction.labs) +
 # geom_point(aes(),stat = "identity", position = position_stack(reverse=TRUE),color="black")+
 #  geom_line( aes(),stat = "identity", position = position_stack(reverse=TRUE),color="black")+
  coord_flip()+
  labs(y = expression(paste("Extracted P (mg gDW"^-1,")" )),
       x = "Depth (cm)",
       title = "Sequential extractions",
       fill = "Extractant"
  ) +
  facet_grid(cols = vars(time), rows = vars(species),
             labeller = labeller(time = time.labs, species = fraction.labs)) +
  theme_bw()+
  theme(
    title = element_text(size = 20),
    axis.title=element_text(size=20),plot.title = element_text(hjust = 0.5),
    axis.text=element_text(size=14,angle = 0, hjust = 0.5),
    legend.title = element_text( size = 20),
    legend.text = element_text(size = 15),
    legend.key.size = unit(1.3, "cm")) 

show(seqextrgroup)

ggsave( "seqextrplot2.png", plot = seqextrgroup, width = 10, height = 5)
```

Only the TP fractions.
```{r }
tpfrac <- allfrac %>% filter(str_detect(Fraction, "TP"))
```

The NRP is calculated forNaOH, by subtracting the SRP from the TP.
```{r }
mutfrac <- bind_cols(
  rename(
    filter( allfrac, species == "NaOH TP" ), TP = cont),
  select( rename(
    filter( allfrac, species == "NaOH SRP" ), SRP = cont), SRP) 
  ) %>%  
  mutate(cont = case_when( TP-SRP <= 0 ~ 0,
                           T ~ TP-SRP
                           ),
         species = replace(species, species == "NaOH TP", "NaOH NRP")) %>% 
  select(species,Depth,time,cont) %>% 
  bind_rows(select(filter(allfrac, species != "NaOH TP" & species != "H2O SRP", species != "Bipy SRP"), !stdev)) %>% 
  filter(time == "10month")


  pivot_wider(names_from = Fraction, values_from = cont) 


  mutate(Total = Total - .data[["H2O TP"]]- .data[["Bipy TP"]]- .data[["BD TP"]]- .data[["NaOH TP"]]- .data[["NaOH SRP"]]) %>% 
  pivot_longer(2:7, names_to = "Fraction", values_to = "cont")
```
### Lables and colours
```{r }
legend_labels <- c( "H2O TP",
                    "Bipyridine; ",
                    "BD; ",
                    "NaOH; SRP" ,
                    "NaOH; NRP" ,
                    "Total P")
                      
colors <- list(c("palegreen2" ,  "tomato3", "plum3", "darkgoldenrod1", "tan3", "burlywood2","goldenrod"),
               c("orange","coral4", "darkorange2","darkgoldenrod1","goldenrod"),
               c( "palegreen2" ),
               c("orange","coral4", "darkorange2","darkgoldenrod1","goldenrod"))
```

### plot the sequential extractions
```{r, fig.dim = c(8, 10)}
seqextr <- ggplot( transform( mutfrac, 
                   species = factor(species, 
                                       levels = c("H2O TP","Bipy TP","BD TP","NaOH SRP","NaOH NRP")
                                       ),
                   time = factor(time, levels = (c("2month", "10month")))), 
       aes( 
           x=Depth),
       scale_x_discrete(position = 'top')) +
  geom_col(
    mapping = aes( y = cont, fill = species ),
    stat = "identity", position = position_stack(reverse=TRUE))+
  scale_fill_manual(values = colors[[1]], labels = legend_labels, name = "Extracted Fraction") +
 # geom_point(aes(),stat = "identity", position = position_stack(reverse=TRUE),color="black")+
 #  geom_line( aes(),stat = "identity", position = position_stack(reverse=TRUE),color="black")+
  coord_flip()+
  scale_x_reverse() + 
  labs(y = expression(paste("Extracted P (mg gDW"^-1,")" )),
       x = "Depth (cm)"
  ) +
  facet_grid(cols = vars(time)) +
  theme_bw()+
  theme(
    axis.title=element_text(size=20),plot.title = element_text(hjust = 0.5),
    axis.text=element_text(size=16,angle = 0, hjust = 0.5),
    legend.title = element_text( size = 20),
    legend.text = element_text(size = 15),
    legend.key.size = unit(1.3, "cm")) 
show(seqextr)

ggsave( "seqextrplot.png", plot = seqextr, width = 10, height = 10)
```

## Fe/P ratio 

```{r}
Fedat <- filter(conc, Parameter == "Fe" | Parameter == "TP" ) %>%  
  filter( Fraction == "BD" | Fraction == "Bipy" ) %>% 
  remove_missing() %>% 
  group_by(Fraction, Parameter,  Depth, time) %>% 
  summarise(stdev = sd(cont), cont = mean(cont) ) 

FePratio <- select(Fedat, !stdev ) %>%  
  pivot_wider( names_from = Parameter, values_from = cont) %>% 
  mutate(FeP = (Fe/55.845)/(TP/30.97))

```


```{r }
ggplot( Fedat, 
         mapping = aes(
           y = cont,
           x = Depth,
          color = time)
) +
   
  geom_line()  +
  geom_point(size = 2) +
  geom_errorbar(aes(ymin=cont-stdev, 
                    ymax=cont+stdev,
                   ), width=.2,
                position=position_dodge(0.05))+
  facet_grid(cols = vars(Fraction), rows = vars(Parameter) )  +
  #geom_point( data = beforebipy, aes( y = cont, x = 0),color="black")+

  xlab("Depth (cm)") +
  scale_x_reverse() +
  coord_flip() +
  labs(  y = expression(paste("concentration (percent dw)")), 
         x = "Depth in cm",
         title = "Fe profiles" ) +
  theme_bw() +
  theme(axis.title=element_text(size=20),
                   plot.title = element_text(size=20, face="bold", hjust = 0.5) ,
                   axis.text=element_text(size=14,angle = 0, hjust = 0.5),
                   legend.title = element_text(size = 16),
                   legend.text = element_text(size = 13),
                   legend.key.size = unit(1.8, "cm"))
```
```{r }
ggplot( FePratio, 
         mapping = aes(
           y = FeP,
           x = Depth,
          color = time)
) +
   
  geom_line()  +
  geom_point(size = 2) +
  facet_grid(cols = vars(Fraction), scales = "free") +
  #geom_point( data = beforebipy, aes( y = cont, x = 0),color="black")+

  xlab("Depth (cm)") +
  scale_x_reverse() +
  coord_flip() +
  labs(  y = expression(paste("Fe/P")), 
         x = "Depth in cm",
         title = "Fe profiles" ) +
  theme_bw() +
  theme(axis.title=element_text(size=20),
                   plot.title = element_text(size=20, face="bold", hjust = 0.5) ,
                   axis.text=element_text(size=14,angle = 0, hjust = 0.5),
                   legend.title = element_text(size = 16),
                   legend.text = element_text(size = 13),
                   legend.key.size = unit(1.8, "cm"))
```

# XRD

```{r }
xrd <- xrd_raw %>% select(Depth,Nr, "2 month", "10 month") %>% 
  mutate(Depth = Depth +3) %>% 
  pivot_longer(cols = !Depth & !Nr, names_to = "time", values_to = "area")

xrdplot <- ggplot( xrd, 
         mapping = aes(
           y = area,
           x = Depth,
          color = time)
) +
   
  geom_line()  +
  geom_point(size = 2) +
  scale_color_discrete(labels = c("9 months", "2 months")) +
  #facet_grid(cols = vars(time), scales = "free") +
  #geom_point( data = beforebipy, aes( y = cont, x = 0),color="black")+

  xlab("Depth (cm)") +
  scale_x_reverse() +
  coord_flip() +
  labs(  y = expression(paste("2",theta,"/abs")), 
         x = "Depth in cm",
         title = "XRD vivianite relative peak area" ) +
  theme_bw() +
  theme(axis.title=element_text(size=20),
                   plot.title = element_text(size=20, face="bold", hjust = 0.5) ,
                   axis.text=element_text(size=14,angle = 0, hjust = 0.5),
                   legend.title = element_text(size = 16),
                   legend.text = element_text(size = 13),
                   legend.key.size = unit(1.8, "cm"))
show(xrdplot)

ggsave( "XRDplot.png", plot = xrdplot, width = 10, height = 5)

```

# PW profiles 

```{r }

pwdata <- read_xlsx("2022_Harm_Peeper_Arendsee.xlsx", skip = 2 , col_names = TRUE)
pwdata[str_detect(pwdata, "<")] <- 0
pwdata$ID <- pwdata$ID - 10
pwdata <- pwdata %>% select(where(is.numeric)) %>% select(!starts_with("NO") & !Zn) %>% mutate(SRP = SRP/1000, HS = HS/1000)

pwlong <- select(pwdata, c(ID,  Fe,Mn, P,  HS)) %>% pivot_longer(cols = 2:last_col(), names_to = "Parameter", values_to = "Value")

```

```{r, fig.dim = c(50, 10)}
pwplots <- ggplot( transform( pwlong, 
                   Parameter = factor(Parameter, 
                                       levels = c("P","Fe","Mn","SO42-","HS")
                                       )), 
         mapping = aes(
           y = Value,
           x = ID,
          color = Parameter)
) +
   
  geom_line()  +
  geom_point(size = 2) +
  facet_grid(cols = vars(Parameter), scales = "free") +
  #geom_point( data = beforebipy, aes( y = cont, x = 0),color="black")+

  xlab("Depth (cm)") +
  scale_x_reverse() +
  coord_flip() +
  labs(  y = expression(paste("concentration mg/L")), 
         x = "Depth in cm",
         title = "pw profiles" ) +
  theme_bw() +
  theme(      aspect.ratio = 2,
                  axis.title=element_text(size=15),
                  plot.title = element_text(size=20, face="bold", hjust = 0.5) ,
                  axis.text=element_text(size=12,angle = 0, hjust = 0.5),
                  strip.text = element_text(size = 13),
                  legend.title = element_text(size = 15),
                  legend.text = element_text(size = 12),
                  legend.key.size = unit(1.5, "cm"))

show(pwplots)

ggsave( "pwplot2.png", plot = pwplots, width = 10, height = 5)
```

